---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tekton

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Check accessibility](https://img.shields.io/badge/check-accessibility-orange.svg)](https://wave.webaim.org/report#/https://packages.tesselle.org/tekton)
<!-- badges: end -->

**tekton** provides a custom [**pkgdown**](https://pkgdown.r-lib.org/) template for [tesselle](https://www.tesselle.org) packages. Please don't use it for your own package.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("tesselle/tekton")
```

## Usage

Make sure your `_pkgdown.yaml` contains:

``` yaml
template:
  package: tekton
```

To work properly, `tekton` requires the assets and templates in `inst/pkgdown/assets/`. Because of this, you should not set `default_assets: false` in your `_pkgdown.yaml`.
